### 2016-05-20 paper/paper.tex
Fleshing outlines of disc. and ethics

\if0
\section{Discussion}

-Proof of (burnt) bandwidth
-Defenses
-Target server's participation

\subsection{Ethical Considerations}
%¯\\\_(ツ)\_/¯
%\symbol{2544}
\shrug

@@

\subsection{Defenses}
\fi
\section{Defenses}

>>>>

\section{Discussion}

%-Proof of (burnt) bandwidth
%-Defenses
%-Target server's participation

Bitcoin was invented with the goal of creating a decentralized digital currency, 
and to that end has been more sucessful than most imagined. Banks are turning
to ``Blockchain technology'' to solve issues regarding public ledgers.
Primecoin and TorPath use cryptocurrencies to incentivize positive actions.
However, this positivity is not inherent to cryptocurrencies. DDoSCoin demonstrates
malicousness inherent to the currency's design.

DDoSCoin uses proof that the miner connected to a given server a sufficient number 
of times as its proof-of-work. This is an indirect measurement of how much bandwidth
to a given endpoint is being wasted by the miner. This provides a unique challenge
when miners have different bandwidth to a given endpoint at a level beyond their direct 
control. In prior cryptocurrencies, the proof-of-work uses resources entirely under the
miner's control. The extreme of having a unique position to attack a site is being the
target, and having the private key for the site. Having this priveleged position allows 
the target to actively engage in DDoSCoin as a defense. We discuss this further in
Section~\ref{sec:defense}.

An interesting choice in the design of DDoSCoin is that the target-setting is done 
dynamically, and by consensus. A given target can go offline, or in some other way
defend against DDoSCoin at any point. When this happens, the currency cannot stall,
as then no coins could be transacted. This necessitates dynamic target-setting, 
despite how strange it may be to have the ``goalposts'' move on miners. This places
risk in targetting sites that are likely to be removed from the target list, or
\emph{controversial} sites. However, each site has its difficulty adjusted 
individually, the controversial site will be easier to mine a block from as more 
miners shy away, balancing the affect.

While stakeholders have control of the target list, a majority of miners could
use their choice of previous block to veto a given proof-of-stake block. This would
be a fork of the blockchain. If a clear majority treat a block as malformed because
it introduces an undesired domain, then the longer chain wins, and the undesired
domain is not included in the target set, and any blocks mined on the chain with
the vetoed target are not part of the blockchain.

%Jumping the gun on PAY\_TO\_DDOS transactions before they find their way into the block chain
%could be weird. Especially if people start only inserting them as they solve the puzzle.
\todo{Talk about TLS 1.3, signing client controlled values}

\subsection{Ethical Considerations}
%¯\\\_(ツ)\_/¯
%\symbol{2544}
While we acknowlege this work introduces an idea that could be used to incentivize 
malicous behavior, the ethics of this paper are controlled. We only demonstrate a 
proof of concept, and in doing so, only attack websites we have ownership of.
Further, we do not publish the full coin, and keep the source of our proof of concept
closed. We believe it important to fully disclose potential attacks, even those that
require the development of an altcoin to execute. This is especially important in the
face of the impending commitment to the design of TLS 1.3, and compounded by how long 
TLS/SSL protocol versions stay in active use.

\shrug

@@

\subsection{Defenses}
\label{sec:defense}
